# File-based Make for R files

**DISCLAIMER**: This is an experimental repository to generate and visualize Makefile for R projects. It only supports specific conditions (comprehensive arguments are not implemented). Please be careful when you run `make` outside your test repository.

## The idea

`makeR` checks all R scripts in the directory, and determines file dependency based on keys in the R scripts such as `read.csv`, `read_csv`, `source`, `load`... `makeR` determines file target based on keys such as `save.image`, `write.csv`, `ggsave`...

## Description

`makeR` requires GNU make and several R packages:

```{r, eval = F}
install.packages("tidyverse")
install.packages("stringr")
install.packages("visNetwork")
install.packages("processx")
```

## Example

The current directory contains three R scripts (`csv_script1-3.r`) that generate csv files (`data1-3.csv`). `analysis.r` will do some analyses using those csv files and produce a figure (`fig1.png`) and a rda file (`fit.rda`). `make_fun` function makes Makefile based on the above.

```{r}
library(tidyverse)
library(stringr)
library(visNetwork)
library(processx)

# load functions to make a makefile
source("make_make.r")

# load functions to visualize a makefile
source("vis.r")

# make makefile based on files in the current repository
make_fun("Makefile")

# prepare data frame for visualization
plan <- make_dat_fun("Makefile")

# visualize makefile
vis_fun(plan)
```

![File network](network.html)

```{r, echo = FALSE}
vis_fun(plan) %>%
  visSave("network.html")
```

To see the content of Makefile on your terminal:

```{bash}
cat Makefile
```

To make your R project on your terminal:

```{bash}
make
```

To make your R project on your R console:
```{r}
run("make")
```
